---
title: "Lab 1 - Data visualization"
author: "Melissa Rodriguez"
format: pdf
editor: visual
---

## Load Packages

```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(viridis)
```

## Exercise 1

```{r ex-1, message = FALSE}
ggplot(data = midwest, mapping = aes(x = popdensity)) + 
  geom_histogram(binwidth = 10000) +
  labs(x = "County", 
       y = "Population Density", 
       title = "Counties \nvs Population Density")
```
The graph is right-skewed because there is a tail of data on the right. Additionally, there appears to be some outliers in between 50000 and 75000 and another between 75000 and 1000. 

## Exercise 2

(Type your answer to Exercise 2 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)

```{r ex-2, message = FALSE}
ggplot(data = midwest, 
       mapping = aes(x = percollege, y = percbelowpoverty , color = state)) +
  scale_color_viridis_d() + 
  geom_point() +
  labs(x = "People With a College Degree", 
       y = "Percentage Below Poverty", 
       title = "College Degree \nvs Below Poverty")


```

## Exercise 3

There is a negative association between people with a college degree and those below poverty. In most of the states, 5%-20% of 10%-25% of people with a college degree are below poverty. 

## Exercise 4

## Exercise 5

## Exercise 6

## Exercise 7
